Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-11-14 Scripts/Initial_Analysis.Rmd
Addressed comments for first round

@@

# Clean names to match data
Matching_names <- my_path("G","Spatial/SAU", "matching_names.csv", read = T) %>% 
  rename(eezid = eez_id)

@@

@@

####  Year of Eergence Analysis

##### Fig. 2. Accumulative plots

```{r Time_lapse_plot,  eval = T, echo = T}

# Per Stock
stock_da <-  Eme_Res %>% 
  left_join(Neighbours) %>% 
  # distinct(taxon_key,neighbour_id, .keep_all = TRUE) %>% 
  group_by(taxon_key,tresh) %>% 
  summarise(
    taxon_emer = min(emerging_yr)
  ) %>% 
  group_by(taxon_emer,tresh) %>% 
  summarise(
    n_tax = n()
  ) %>% 
  group_by(tresh) %>% 
  mutate(
    com_sum = cumsum(n_tax),
    level = "stock"
  )

# Plot Data
plot_data <- stock_d %>% 
  bind_rows(eez_d) %>% 
  filter(tresh != "NA") %>% 
  mutate(
    total = ifelse(level == "stock",length(unique(Eme_Res$taxon_key)),length(unique(Eme_Res$sf_eez_name))),
    per = com_sum/total*100
  ) %>% 
  gather("metric","value",com_sum,per) %>% 
  filter(tresh == "Tresh_one") %>% 
  mutate(
    my_facet = ifelse(metric == "per","Percentage (%)","Cumulative sum"),
    label = ifelse(total == 478,"Total number of stocks","Total number of EEZs")
  );plot_data

#### Both plots for tresh one

ggplot() +
  geom_area(data = subset(plot_data, level == "stock"),
            aes(
              x = as.numeric(taxon_emer),
              y = value,
              fill = level
            ),
            alpha= 0.8,
            size=0.5,
            colour="black"
  )  +
  geom_area(data = subset(plot_data, level == "eez"),
            aes(
              x = as.numeric(taxon_emer),
              y = value,
              fill = level
            ),
            alpha= 0.8,
            size=0.5,
            colour="black"
  )  +
  geom_line(data = subset(plot_data, metric == "com_sum"),
            aes(
              x = as.numeric(taxon_emer),
              y = total,
              fill = level
            ),
            colour="grey30",
  )  +
  geom_text(data = subset(plot_data, metric == "com_sum"),
            aes(
              x = 2037,
              y = total+5,
              label = label
            ),
            size = 3,
            colour="grey30",
            hjust=0.6,
  )  +
  facet_wrap(~my_facet,
             scales = "free") + 
  scale_y_continuous("",expand = expand_scale(mult = c(0, .05))) +
  scale_x_continuous("Time of emergence",
                     breaks = seq(2000,2100,25),
                     limits = c(2005,2100),
                     expand = c(0, 0)
  ) +
  my_ggtheme_p() +
  theme(
    legend.position = "right"
  ) +
  guides(fill=guide_legend(title= "Level")) +
  scale_fill_viridis(discrete = T,
                     labels = c("EEZs","Stocks")
  ) +
  ggsave("./Figures/cumu_per_freq.png",
         width = 7,
         height = 7,
         units = "in"
  )

@@

##### Fig. 3 Mapping the time of emergence

###### Just mean time

# Per EEZs
Eez_d_hist <- Eme_Res %>% 
  group_by(eezid ,sau_fishing_entity,tresh) %>% 
  # summarise(n_tax = length(unique(taxon_key))) %>% 
  summarise(
    mean_yr = mean(emerging_yr,na.rm=T),
    sd_yr = sd(emerging_yr,na.rm=T),
    n_taxa = length(unique(taxon_key))
    ) %>% 
  gather("metric","value",mean_yr:n_taxa) %>% 
  # filter(metric != "n_taxa") %>% 
  mutate(
    reverse = abs(value-2100)  + 2000
  )

World_map_nemer <- World_map %>%
  left_join(Value_map_data,
            by = c("sau_fishing_entity","fishing_entity_id")
  ) %>% 
  filter(!is.na(participation))

grey_land <- World_map %>% 
  filter(!fishing_entity_id %in% World_map_nemer$fishing_entity_id) %>% 
  filter(sovereignt != "Antarctica")

grey_eez <- World_eez_sf %>% 
  filter(!eezid %in% Eez_d_hist$eezid)

for(i in 1:2){

  ) +
  scale_fill_viridis(option="magma", discrete = T, begin = 0.7) +
  scale_color_viridis(option="magma", discrete = T, begin = 0.7) +
  theme_minimal() + 
  theme(
    panel.background = element_rect(fill = "white", colour = "white"),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text = element_text(size = 12, colour="black"),
    axis.title.x = element_text(size = 12, colour="black", face = "bold"),
    legend.position = ""
  );Eez_hist

  World_map_part <- World_map_nemer %>% 
    filter(
      tresh ==  tresh_list[i], 
      variable == "value"
    )

  map <- World_eez_sf %>% 
    left_join(Eez_d_hist,
              by = "eezid") %>% 
    filter(tresh == tresh_list[i],
           metric == "mean_yr") %>% 
    ggplot() +
    geom_sf(
      aes(
        fill = reverse
      ),
      color =  "white",
      size = 0.1
    ) +
    # Inlcude the participation of species
    geom_sf(data = World_map_part,
            aes(fill = participation+2000),
            color =  "white",
            size = 0.1
            ) +
    # grey maps
    geom_sf(data = grey_land, aes(),fill = "grey50", color =  "white",size = 0.1) +
    geom_sf(data = grey_eez, aes(),fill = "grey50", color =  "white",size = 0.1) +
    # Set Participation labels
    annotate("text", 
             x =-135,
             y = -69,
             label = "Participation (%)", 
             color="black", 
             size=4, 
             angle=0, 
             fontface="bold",
             hjust=0) +
    annotate("text", 
             x = c(-76,-35,6,48,88),
             y = -69,
             # x =(c(-8500000,-3000000,2500000,7500000,12800000)),
             # y = -9050000,
             label = c(0,25,50,75,100), 
             color="black", 
             size=4, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    # Set ToE labels
    annotate("text", 
             x =-135,
             y = -85,
             label = "Time of Emergence",
             color="black", 
             size=4, 
             angle=0, 
             fontface="bold",
             hjust=0) +
    annotate("text", 
             x = c(-79,-39,3,45,87),
             y = -85,
             label = seq(2100,2000,-25), 
             color="black", 
             size=4, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    scale_fill_viridis("",
      limits = c(2000,2100),
      breaks = seq(2000,2100,25),
      labels = c("","","","","")#,
      # direction = -1
    ) +
    # geom_hline(yintercept = c(-50,0,50,80)) +
    my_ggtheme_m() +
    theme(
      legend.box.margin = margin(t = -64, l = 229),
      legend.text = element_blank(),
      legend.key.width = unit(5, "line")
    )

  p <- ggdraw() +
    # ToE Latitudinal plot
    draw_plot(Eez_hist, x = 0.873, y = 0.13, width = 0.124, height = 0.77) +
    # Time of Emergence Map
    draw_plot(map, x = 0, y = 0, width = 0.95, height = 1)

  save_plot(
    name_save,
    p,
    base_height = 6,
    base_width = 12
  )

# Plot the bubbles!
ggplot(Buble_data) +
  geom_point(
    aes(
      x = mean_yr,
      y = log_value,
      size = n_taxa,
      colour = un_geo_region
    ),
    alpha = 0.7
  ) +
  # Divisory lines
  geom_vline(xintercept = 2030, color = "grey90", size = 0.5) +
  geom_hline(data = Percentile_value,
             aes(yintercept = x),
             color = "grey90"
  )  +
  geom_label_repel(data = subset(Buble_data, sum_value_bi >= 1),
                   aes(
                     x = mean_yr,
                     y = log_value,
                     label = sau_fishing_entity
                   ),
                   arrow = arrow(length = unit(0.009, "npc"),
                                 type = "closed",
                                 ends = "first"),
                   force = 2,
                   box.padding = 1,
                   fill = "NA"

#### Fig. 5 Boxplot

Dem_pel <- Eme_Res %>% 
  filter(tresh == "Tresh_one",
         !is.na(un_sub_region)) %>% 
  left_join(Spp_env_pref) %>% 
  mutate(DemersPelag = ifelse(is.na(DemersPelag),"other",
                              ifelse(DemersPelag %in% c("bathypelagic","benthopelagic"), "bathy-bentho-pelagic",paste(DemersPelag)
                              )
  ),
    un_sub_region = ifelse(str_detect(un_sub_region,"Latin"),"Ltn. Ame. and the Car.",paste(un_sub_region)))

## Averages

Average_data <- Dem_pel %>% 
  group_by(un_sub_region) %>% 
  summarise(mean_toe = mean(emerging_yr,na.rm=T)) %>% 
  mutate(regional_average="regional average")

# Dem Pelagic boxplot
ggplot(Dem_pel) +
  geom_hline(data = Average_data,
             aes(
               yintercept = mean_toe,
               colour = regional_average
             ),
             linetype = "dashed"
             ) +
  geom_boxplot(
    aes(
      x = reorder_within(DemersPelag,emerging_yr,un_sub_region),
      y = emerging_yr,
      fill = DemersPelag
    ),
    alpha = 0.8
  ) +
  facet_wrap(~un_sub_region,scales = "free_x") +
  scale_fill_viridis("Habitat preference",
                     discrete = T) +
  scale_color_grey("") +
  xlab("") +
  ylab("Time of emergence") +
  my_ggtheme_p() +
  theme(
    axis.text.x = element_blank(),
    axis.ticks.x = element_blank(),
    legend.position = "right"
  ) +
  scale_x_reordered() +
  ggsave("./Figures/regional_hab_boxplot.png",
         width = 14,
         height = 8,
         units = "in"
  )
```

## Table.1 Multy linear model

>>>>

# ------------------------------------------- #
### Estimate number of transboundary stocks ###
# ------------------------------------------- #

Transboundary_spp %>% 
  left_join(Neighbours,
            by = c("eez_name", "eez_neighbour")) %>% 
  # filter(neighbour_id %in% c(1,105)) %>%
  # filter(neighbour_id == 470) %>%
  group_by(neighbour_id) %>% 
  summarise(n_stock = length(unique(taxon_key))) %>% 
  # View()
  group_by() %>% 
  summarise(t_trans_stocks = sum(n_stock)) # 9132

@@

# Clean names to match data
Matching_names <- my_path("G","Spatial/SAU", "sau_matching_names.csv", read = T) %>% 
  rename(eezid = eez_id)

@@

###  Year of Eergence Analysis

```{r ToE_generals,  eval = T, echo = T}

# Total number of emerging stocks

# Global estimates
Eme_Res %>% 
  group_by(tresh,neighbour_id) %>% 
  summarise(
    emerging_stocks = length(unique(taxon_key))
    ) %>% 
  group_by(tresh) %>% 
  summarise(
    emerging_stocks = sum(emerging_stocks),
    prop_total = (emerging_stocks/9132)*100,
    )

# Global average ToE
Eme_Res %>% 
  group_by(tresh) %>% 
  summarise(
    # emerging_stocks = length(unique(taxon_key)),
    # prop_total = (emerging_stocks/9132)*100,
    mean= mean(emerging_yr),
    sd = sd(emerging_yr),
    min = min(emerging_yr),
    max = max(emerging_yr)
           )

##### Fig. 1. Accumulative plots

```{r Time_lapse_data,  eval = T, echo = T}

# Per Stock
stock_d <-  
  Eme_Res %>% 
  left_join(Neighbours) %>% 
  # distinct(taxon_key,neighbour_id, .keep_all = TRUE) %>% 
  group_by(taxon_key,neighbour_id,tresh) %>% 
  summarise(
    taxon_emer = min(emerging_yr)
  ) %>% 
  group_by(taxon_emer,tresh) %>% 
  summarise(
    n_tax = n()
  ) %>% 
  group_by(tresh) %>% 
  mutate(
    com_sum = cumsum(n_tax),
    level = "stock"
  )

max(stock_d$com_sum)

max(eez_d$com_sum)

# Plot Data
plot_data <- stock_d %>% 
  bind_rows(eez_d) %>% 
  filter(tresh != "NA") %>% 
  mutate(
    # total = ifelse(level == "stock",length(unique(Eme_Res$taxon_key)),length(unique(Eme_Res$sf_eez_name))),
    total = ifelse(level == "stock",max(stock_d$com_sum),max(eez_d$com_sum)),
    per = com_sum/total*100
  ) %>% 
  gather("metric","value",com_sum,per) %>% 
  filter(tresh == "Tresh_one")

# Manually include rest of EEZs

cont_eez <- plot_data %>% 
  filter(level == "eez") %>% 
  slice(1:36) %>%
  select(-1) %>% 
  mutate(
    value = ifelse(metric == "per",100,232),
    taxon_emer = c(seq(2082,2099,1),seq(2082,2099,1))
  )

plot_data <- plot_data %>% 
  bind_rows(cont_eez) %>% 
  mutate(
    my_facet = ifelse(metric == "per","Percentage (%)","Cumulative sum (n stocks)"),
    label = ifelse(total == max(stock_d$com_sum),"Total number of emerging stocks","Total number of EEZs")
  )

# How many between 2006 and 2020?
plot_data %>% 
  filter(taxon_emer <= 2020,
         tresh == "Tresh_one") %>% 
  group_by(level,metric) %>% 
  summarise(
    max(taxon_emer),
    min(taxon_emer),
    max(taxon_emer),
    min(taxon_emer)
  )

# Percentage increase of EEZ after 2020
lm_eez <- plot_data %>% 
  filter(taxon_emer <= 2020,
         tresh == "Tresh_one",
         metric == "per")

summary(lm(lm_eez$taxon_emer~lm_eez$value))

```{r Time_lapse_plot}
#### Both plots for tresh one

ggplot() +
  geom_area(data = subset(plot_data, level == "eez"),
            aes(
              x = as.numeric(taxon_emer),
              y = value,
              fill = level
            ),
            alpha= 0.5,
            size=0.5,
            colour="black"
  )  +
  geom_area(data = subset(plot_data, level == "stock"),
            aes(
              x = as.numeric(taxon_emer),
              y = value,
              fill = level
            ),
            alpha= 0.5,
            size=0.5,
            colour="black"
  )  +
  # geom_line(data = subset(plot_data, metric == "com_sum"),
  #           aes(
  #             x = as.numeric(taxon_emer),
  #             y = total,
  #             fill = level
  #           ),
  #           colour="grey30",
  # )  +
  # geom_text(data = subset(plot_data, metric == "com_sum"),
  #           aes(
  #             x = 2037,
  #             y = total+5,
  #             label = label
  #           ),
  #           size = 3,
  #           colour="grey30",
  #           hjust=0.6,
  # )  +
  facet_wrap(~my_facet,
             scales = "free") + 
  scale_y_continuous("",expand = expand_scale(mult = c(0, .05))) +
  scale_x_continuous("Time of emergence",
                     breaks = seq(2000,2100,25),
                     limits = c(2005,2100),
                     expand = c(0, 0)
  ) +
  my_ggtheme_p() +
  theme(
    legend.position = "right"
  ) +
  guides(fill=guide_legend(title= "Level")) +
  scale_fill_viridis(discrete = T,
                     labels = c("EEZs","Stocks")
  ) +
  ggsave("./Figures/cumu_per_freq.png",
  width = 12,
  height = 7,
  units = "in"
  )

##### Fig. 2 Mapping the time of emergence

###### Mean ToE and vulnerabillity Index

# Per EEZs
Eez_d_hist <- Eme_Res %>% 
  group_by(eezid,sau_fishing_entity,tresh) %>% 
  # summarise(n_tax = length(unique(taxon_key))) %>% 
  summarise(
    mean_yr = mean(emerging_yr,na.rm=T),
    sd_yr = sd(emerging_yr,na.rm=T),
    n_taxa = length(unique(taxon_key))
    ) %>% 
  gather("metric","value",mean_yr:n_taxa) %>% 
  # filter(metric != "n_taxa") %>% 
  mutate(
    reverse = abs(value-2100)  + 2000
  )

### ----------------- ###
### Index alternative ###
### ----------------- ###

Index_data <- Eez_d_hist %>% 
  left_join(Value_map_data) %>% 
  filter(
    tresh == "Tresh_one",
    metric == "mean_yr"
  ) %>% 
  group_by(sau_fishing_entity,fishing_entity_id,variable) %>% 
  summarise(
    toe = mean(value,na.rm=T),
    # sum_value = sum(sum_value),
    mean_part = mean(participation,na.rm=T)
  ) %>% 
  filter(!is.na(variable)) %>% 
  # spread(variable,sum_value) %>% 
  spread(variable,mean_part) %>% 
  mutate(
    imp = catch+value,
    index = imp/toe
  )

##### Normalize index
# https://www.datanovia.com/en/blog/how-to-normalize-and-standardize-data-in-r-for-great-heatmap-visualization/

# Get min and maximums
min_index <- min(Index_data$index)
max_index <- max(Index_data$index)

Index_data <- Index_data %>% 
  mutate(
    index_norm =(index-min_index)/(max_index-min_index),
    index_2000 = 2000 + (index-min_index)*(2100-2000)/(max_index-min_index)
  )

### Explore index ####

# ggplot(data = Index_data) +
#   geom_point(
#     aes(
#       x = toe,
#       y = imp,
#       color = index_2000
#     ),
#     size = 4
#   ) +
#    scale_color_viridis(option="magma", discrete = F)

#### ------------  ####

Value_map_data <- Index_data %>%
  select(sau_fishing_entity,fishing_entity_id,
         # tresh,
         # variable,
         participation = index_2000)

### ----------------- ###

World_map_nemer <- World_map %>%
  full_join(Value_map_data,
            by = c("sau_fishing_entity","fishing_entity_id")
  ) %>% 
  filter(!is.na(participation))

# These are regions without transboundary species
grey_land <- World_map %>% 
  filter(!fishing_entity_id %in% Value_map_data$fishing_entity_id) %>% 
  filter(!sovereignt %in% c("Antarctica","Brazil"))

grey_eez <- World_eez_sf %>% 
  filter(!eezid %in% Eez_d_hist$eezid,
         !eez_name %in% Neighbours$eez_name)

Brazil_land <- World_map %>% 
  filter(sovereignt == "Brazil")

Brazil_eez <- World_eez_sf %>% 
  filter(eez_name %in% c("Brazil","USA (Alaska, Arctic)"))

for(i in 1:1){

  ) +
  scale_fill_viridis(option="magma", discrete = T, begin = 0.7) +
  scale_color_viridis(option="magma", discrete = T, begin = 0.7) +
  theme_minimal() + 
  theme(
    panel.background = element_rect(fill = "white", colour = "white"),
    panel.grid.major.y = element_blank(),
    panel.grid.minor.y = element_blank(),
    panel.grid.major.x = element_blank(),
    panel.grid.minor.x = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    axis.text = element_text(size = 12, colour="black"),
    axis.title.x = element_text(size = 12, colour="black", face = "bold"),
    legend.position = ""
  )

  World_map_part <- World_map_nemer# %>% 
    # filter(
    #   tresh ==  tresh_list[i], 
    #   variable == "value"
    # )

  map <- World_eez_sf %>% 
    left_join(Eez_d_hist,
              by = "eezid") %>% 
    filter(tresh == tresh_list[i],
           metric == "mean_yr") %>% 
    ggplot() +
    geom_sf(
      aes(
        fill = reverse #original map
        # fill = value
      ),
      color =  "white",
      size = 0.1
    ) +
    # Inlcude the participation of species
    geom_sf(data = World_map_part,
            # aes(fill = participation+2000), #original map
            aes(fill = participation),
            color =  "white",
            size = 0.1
            ) +
    # grey maps
    # ggplot() +
    geom_sf(data = grey_land, aes(), fill = "grey50", color =  "white",size = 0.1) +
    geom_sf(data = grey_eez, aes(), fill = "white", color =  "grey50",size = 0.1) +
    geom_sf(data = Brazil_eez, aes(), fill = "lightblue", color =  "white",size = 0.1) +
    geom_sf(data = Brazil_land, aes(), fill = "lightblue", color =  "white",size = 0.1) +
    # Set Participation labels
    annotate("text",
             x =-135,
             y = -69,
             label = "Vulnerabillity index",
             color="black",
             size=4,
             angle=0,
             fontface="bold",
             hjust=0) +
    annotate("text", 
             x = c(-76,-35,6,48,88),
             y = -69,
             # x =(c(-8500000,-3000000,2500000,7500000,12800000)),
             # y = -9050000,
             label = c(0,25,50,75,100), 
             color="black", 
             size=4, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    # Set ToE labels
    annotate("text", 
             x =-135,
             y = -85,
             label = "Time of Emergence",
             color="black", 
             size=4, 
             angle=0, 
             fontface="bold",
             hjust=0) +
    annotate("text", 
             x = c(-79,-39,3,45,87),
             y = -85,
             label = seq(2100,2000,-25), # original
             # label = c(">2100",seq(2075,2000,-25)), # not inluding the > because we dont know
             color="black", 
             size=4, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    scale_fill_viridis("",
      limits = c(2000,2100),
      breaks = seq(2000,2100,25),
      labels = c("","","","","")#,
      # direction = -1
    ) +
    # scale_fill_gradientn("",
    #                      limits = c(2000,2100),
    #                      breaks = seq(2000,2100,25),
    #                       labels = c("","","","",""),
    #                      colours = pal
    # ) +
    # geom_hline(yintercept = c(-50,0,50,80)) +
    my_ggtheme_m() +
    theme(
      legend.box.margin = margin(t = -64, l = 229),
      legend.text = element_blank(),
      legend.key.width = unit(5, "line")
    )

  ## --------------- ##
  # Regional Boxplot
  ## --------------- ##

  boxplot <- Eme_Res %>% 
    filter(tresh == "Tresh_one",
           !is.na(un_sub_region)) %>%
    group_by(un_sub_region) %>% 
    summarise(order = median(emerging_yr)) %>% 
    left_join(Eme_Res) %>% 
    filter(tresh == "Tresh_one",
           !is.na(un_sub_region)) %>% 
    mutate(un_sub_region = ifelse(str_detect(un_sub_region,"Latin"),"Ltn. Ame. and the Car.",paste(un_sub_region))) %>% 
    ggplot() +
    geom_boxplot(
      aes(
        # x = un_sub_region,
        x = reorder(un_sub_region,order),
        y = emerging_yr#,
        # fill = un_geo_region
      ),
      fill = "grey"
    ) +
    facet_wrap(~un_geo_region,
               scales = "free_x",
               nrow = 1) +
    scale_fill_viridis("UN Sub region",
                       discrete = T) +
    scale_color_grey("") +
    xlab("") +
    ylab("Time of Emergence") +
    my_ggtheme_p() +
    theme(
      axis.text.x = element_text(size = 10, angle = 45, face = "plain", hjust = 1), 
      strip.text.x = element_text(size = 14, colour = "black"), 
      # axis.ticks.x = element_blank(),
      legend.position = "right"
    )

  p <- ggdraw() +
    # ToE Latitudinal plot
    draw_plot(Eez_hist, x = 0.873, y = 0.53, width = 0.124, height = 0.37) +
    # Time of Emergence Map
    draw_plot(map, x = 0, y = 0.4, width = 0.95, height = 0.6) +
    # Regional boxplot
    draw_plot(boxplot, x = 0, y = -0.03, width = 1, height = 0.44) +
    # Labels
    draw_plot_label(label = c("A", "B"), 
                      size = 20,
                      x = c(0, 0), 
                      y = c(0.95, 0.46)
      )

  save_plot(
    name_save,
    p,
    base_height = 11,
    base_width = 12
  )

# Plot the bubbles!
ggplot(Buble_data) +
  geom_point(
    aes(
      x = mean_yr,
      y = log_value,
      size = n_taxa,
      # colour = un_geo_region,
      shape = un_geo_region
    ),
    alpha = 0.7
  ) +
  # Divisory lines
  geom_vline(xintercept = 2030, color = "grey90", size = 0.5) +
  geom_hline(data = Percentile_value,
             aes(yintercept = x),
             color = "grey90"
  )  +
  geom_label_repel(data = subset(Buble_data, sum_value_bi >= 1),
                   aes(
                     x = mean_yr,
                     y = log_value,
                     label = sau_fishing_entity
                   ),
                   arrow = arrow(length = unit(0.009, "npc"),
                                 type = "closed",
                                 ends = "first"),
                   force = 2,
                   box.padding = 1,
                   fill = "NA"

#### Fig. 5 Species Boxplot

# Dem Pelagic boxplot
Eme_Res %>% 
  left_join(Spp_env_pref) %>% 
  mutate(DemersPelag = ifelse(is.na(DemersPelag),"other",DemersPelag)) %>% 
  group_by(DemersPelag) %>% 
  summarise(mean_toe = median(emerging_yr,na.rm=T),
            n_spp = length(unique(taxon_key))) %>% 
  left_join(Dem_pel) %>% 
  mutate(
    label = paste0(DemersPelag, "\n(n=",n_spp,")")
  ) %>% 
  filter(tresh == "Tresh_one",
         DemersPelag != "pelagic") %>% # just one spp.
  ggplot() +
  geom_boxplot(
    aes(x = reorder(label,mean_toe),
        # aes(x = DemersPelag,
        y = emerging_yr,
        # fill = DemersPelag
    ),
    alpha = 0.8,
    fill = "grey"
  ) +
  # scale_fill_viridis("Habitat preference",
                     # discrete = T) +
  xlab("") +
  ylab("Time of emergence") +
  my_ggtheme_p() +
  theme(
    axis.text.x = element_text(size = 10, angle = 45, face = "plain", hjust = 1), 
    # axis.ticks.x = element_blank(),
    legend.position = "right"
  ) +
  scale_x_reordered() +
  ggsave("./Figures/regional_hab_boxplot.png",
         width = 10,
         height = 5,
         units = "in"
  )

@@

@@

###### Table.1 Multy linear model
